Figures

### 2019-09-06 manuscript/figures.Rmd
update fig captions

```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-comparison-1.pdf")
```

```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics{"../tables/03_model_summary"}', col.names = NULL, caption = "Model selection diagnostics")
```

@@

```{r re-1, fig.cap = "Hydrologic region level effect of watershed land use for the best performing model for TP and TN respectively. Values that do not overlap the population level median are shaded in red.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-1.pdf")
```

```{r tn_re_hu4-1, fig.cap = "Map highlighting corn sensitive regions from the previous figure.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tn_re_hu4-1.pdf")
```

>>>>

```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN. Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines). Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-comparison-1.pdf")
```

```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient. Table is sorted by decreasing R2 and expected log predictive density.")
```

@@

```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover on A) TP and B) TN. Lines shown are 95% credible intervals with median marked by a filled circle. Values that do not overlap the population level estimate are shaded in red.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-1.pdf")
```

```{r tn_re_hu4-1, fig.cap = "Location of hydrologic regions sensitive to watershed land-use cover corresponds to highlighted credible intervals in Figure 4.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tn_re_hu4-1.pdf")
```
